%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{3cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Berenice} % Your first name
\familyname{Venegas Cotero} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Resume}
%\address {}{Philadelphia, PA}
\mobile{(267) 584 8564}
\email{berenice@cotero.org}
\homepage{blog.cotero.org}{blog.cotero.org} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\homepage{https://github.com/clamorisse}{github: clamorisse}
\extrainfo{github: clamorisse}
\quote{DevOps Engineer - AWS Developer Associate certified\newline
Interested in building distributed system in the cloud, reliable, scalable and fully automated.\newline
Eager to work on a challenging project}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\cvitem{Cloud}{AWS: Networking, Security, DB, ECS, Autoscaling, ELB  }
\cvitem{DevOps}{CloudFormation, Terraform, Consul, Docker, }
\cvitem{Automation}{Atlas, Vault, Rspec/Serverspec, TestKitchen, Chef, unit testing}
\cvitem{CI/CD}{Git, CircleCI, Jenkins}
\cvitem{Scripting}{\textsc{bash}, \textsc{python}, \textsc{ruby}}
\cvitem{Other}{Ansible, \textsc{C++}, \textsc{Javascript}, \textsc{R}}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

%\subsection{Vocational}

\cventry{2015--Present}{AWS consultant}{}{Philadelphia}{}{Created reliable, scalable and fully automated AWS infrastructure as code using Terraform. Special attention to following best practices.{}
\begin{itemize}
\item HPC cluster to run on demand {\textsc{CHARM}} simulations in AWS. 
\item Migration of WebSites to AWS: WordPress and Hugo.
\end{itemize}}

%------------------------------------------------

\cventry{2011--2015}{Data Scientist}{\textsc{Temple University}}{Philadelphia}{}{
\begin{itemize}
\item  Applied multivariate analysis and statistical inference to correlate lipid profile samples with pathologies.
\item Applied Bayesian statistics in proteomic and lipidomic profiles to find patterns that would predict anomalies associated with pathologies.
\end{itemize}}

%------------------------------------------------

\cventry{2009--2011}{Associate Scientist}{\textsc{Temple University School of Medicine}}{Philadelphia}{}{
\begin{itemize}
\item Produced liposomal nano-particle that efficiently controlled drug leakage.
\item Manipulated surface characteristics of nano-particle.
\item Developed a simulations in R to predict surface distribution and diffusion of lipids.
\end{itemize}}

%------------------------------------------------

\cventry{2006--2009}{Associate Scientist}{\textsc{Temple University College of Engineering}}{Philadelphia}{}{
\begin{itemize}
\item Produced a targeted delivered liposomal nano-particle for mammary cancer tumors.
\item Performed pharmacological analysis to calculate circulation and particle retention times.
\item Created a custom image analysis to transform 2D fluorescence images of tumors into the 3D tumor/organ fluoresce source to determine actual dye concentration.
\end{itemize}}

%------------------------------------------------

\subsection{Postdoctoral Residences}

\cventry{2003--2006}{Lipid lateral distribution in model membranes}{\textsc{Temple University School of Medicine}}{Philadelphia}{}{
\begin{itemize}
\item Established a standardized method to detect regularly distributed lipids in model membranes.
\item Characterized the critical factors that will affect their detection. 
\item Utilized custom algorithms to performed statistical data analysis.
\item Developed a Monte Carlo simulation in C++ to validate the experimental results.
\end{itemize}}

%------------------------------------------------

\cventry{2003}{Improve patch-clamp infrastructure}{\textsc{Temple University School of Medicine}}{Philadelphia}{}
{\begin{itemize}
\item Implemented a brand new setting to cut costs and enhance efficiency of a patch-clamp circuitry. The goal was to reduce the noise level and be able to detect changes of 2pAmpers accurately.
\end{itemize}}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{1997--2003}{Ph.D. Biophysics}{Universidad Autónoma del Estado de Morelos}{Mexico}{Awarded with Honors} {
\begin{itemize}
\item Recorded single channel of antimycotic AmB using patch-clamp electrophysiology.
\item Determined the conditions for maximal appearance of AmB channels.
\item Developed an algorithms and coded in C++ to find the different levels of currents and open time intervals of the channels. 
\item Describe the function of AmB channels as function of membrane properties using statistical analysis.
\end{itemize}}

\cventry{1991--1997}{Physics--Astronomy}{Universidad Autónoma de Baja California}{Mexico}{}{
\begin{itemize}
\item Awarded the "Early start in research fellowship" for the project: Dynamical simulations to determine the trajectory memory length in n-body interactions.
\item Performed numerical simulations in C++.
\end{itemize}}



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards and Certifications}

\cvitem{2016}{Diversity Fellowship -- DockerCon}
\cvitem{2016}{AWS -- Developer Associate}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Presentations}

\cventry{1998-present}{Presenter}{Physics and Biophysics}{}{}{National and International Meetings}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Spanish}{Mothertongue}{}
\cvitemwithcomment{English}{Proficient}{}
\cvitemwithcomment{Portuguese}{Intermediate}{}
\cvitemwithcomment{French}{Basic}{}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}